---
title: "Analysis"
output: html_document
date: "2024-03-01"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)

load('/Users/arthurvaz/Desktop/CEFETRJ - Mestrado/Anomalia/Anomalia/kmeans/kmeans_result.RData')
```

## EDA

Undestending how the data is distributed in the Kmeans result file.

-  Number of windows detected sorted by variable

```{r analyse1, echo=FALSE}
df_final %>% group_by(variable) %>% summarise(n = n()) %>% arrange(desc(n))
```

The variable f1 has the most windows detected.

- Number of sizes of windows detected

```{r analyse2, echo=FALSE}
df_final %>% group_by(seq) %>% summarise(n = n()) %>% arrange(desc(n))
```
The size 30 has the most windows detected.

- Average recall and precision by variable

```{r analyse3, echo=FALSE}
df_final %>% group_by(variable) %>% summarise(mean_recall = mean(recall), mean_precision = mean(precision)) %>% arrange(desc(mean_precision))
```

The redox variable demonstrates the highest average precision, indicating that the model excels in detecting anomalies within this variable. However, across all variables, the model experiences a significant number of false negatives due to window size limitations, as the example fails to explore anomaly sequence cases.

- Average recall and precision by size

```{r analyse4, echo=FALSE}
df_final %>% group_by(seq) %>% summarise(mean_recall = mean(recall), mean_precision = mean(precision)) %>% arrange(desc(mean_precision))

```

Size 15 exhibited superior performance in both precision and recall, despite the fact that size 5 has a smaller window size effect compared to 15.

## Conclusion

The variable with a window size of 10 exhibits the highest average precision and recall, making it a promising starting point for enhancing the model.

```{r analyse5, echo=FALSE}

# Convert seqlen to a factor
df_final$seqlen <- factor(df_final$seqlen)

# Check unique values in the seqlen variable
unique_seqlen <- unique(df_final$seqlen)

# Determine the number of unique seqlen values
num_unique_seqlen <- length(unique_seqlen)

# Create a scatter plot using scale_shape_manual
scatter_plot <- ggplot(df_final, aes(x = recall, y = precision, color = variable, shape = seqlen)) +
  geom_point() +
  labs(x = "Recall", y = "Precision", color = "Variable", shape = "Seqlen") +
  scale_shape_manual(values = 1:num_unique_seqlen) +  # Assign shapes manually
  ggtitle("Gecco Kmeans result: Precision vs. Recall") +  # Add a title
  theme_minimal()

# Show the scatter plot
print(scatter_plot)

```